%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Manohar Palanisamy} \\ \vspace{6pt}
    \small \raisebox{-0.1\height}\faPhone\  +91-9819876078 ~
     \href{mailto:manoharpalanisamy@icloud.com}{\raisebox{-0.2\height}\faEnvelope\ \textcolor{MidnightBlue}{\underline{manoharpalanisamy@icloud.com}}} ~ 
     \href{https://decodeai.in/}{\raisebox{-0.2\height}\faUser\ \textcolor{MidnightBlue}{\underline{www.decodeai.in}}} ~
    \href{https://linkedin.com/in/manoharpalanisamy}{\raisebox{-0.2\height}\faLinkedin\ \textcolor{MidnightBlue}{\underline{linkedin.com/in/manoharpalanisamy}}}  ~
   
\end{center}


%-----------EXPERIENCES-----------
\section{WORK EXPERIENCES}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Associate - Machine learning}{Dec 2023 -- Dec 2018}
      {Sevasys Technologies}{Bangalore}
      \resumeItemListStart
    \resumeItem{
      Contributed to POC projects in Generative AI, implementing end-to-end ML solutions with OpenAI, Langchain, \\Gemini AI and Open source models like Huggingface.
    }
  \resumeItem{
    Collaborated cross-functionally to brainstorm, prototype, and iterate ML solutions, gaining practical experience in real-world applications.
    } 
\resumeItem{Integrated ML models into existing systems, optimizing performance and scalability for production deployment.}  
\resumeItem{
Contributed to team efforts in research and development, staying abreast of the latest advancements in \\machine learning technologies.
}
    \resumeItemListEnd



    \resumeSubheading
      {Executive Software Developer}{Dec 2018 -- Jan 2017}
      {QuantumLink Communications Pvt Ltd}{Mumbai}
      \resumeItemListStart
      \resumeItem{
      Developed a research-based web application called FieldSense. This project involved creating a Salesforce tracking system to monitor salesperson activities.
      }
      \resumeItem{
Responsible for handling feature enhancement and \textit{bug }fixing related to our products which also included understanding the requirements and preparing design documents and Impact Analysis.}

\resumeItem{
Worked on an email system with full knowledge of network and email protocols, ensuring timely delivery and quality, all in line with the client's quality standards.
}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
    \item{
        
        \textbf{Generative AI:} OpenAI, Langchain, HuggingFace, Google Generative AI, \\
        \vspace{0.15cm}
        \textbf{Artificial Neural Networks:} Perceptron, MLP, CNN, RNN, LSTM, GRU, BRNN, Autoencoders, GAN, Residual Net, Transformers, ChatGPT, Gemini Pro, Gemini Pro Vision.  \\
        \vspace{0.15cm}
        \textbf{ML Model And Algorithms:} Linear Regression, Logistic Regression, SVM, Gradient Descent, SGD, minibatch GD, Adam etc. \\
        \vspace{0.15cm}
        \textbf{Coding Skills:} Scripting and web development including Python (NumPy, scikit-learn) , Streamlit, Java, REST API, HTTP Server, Mail protocols and DNS server \\
        \vspace{0.15cm}

        \textbf{Deep Learning Frameworks:} TensorFlow, Keras, PyTorch \\
        \vspace{0.15cm}
        \textbf{Natural Language Processing:} NLTK (Natural Language Toolkit), spaCy \\
        \vspace{0.15cm}
        \textbf{Model Evaluation:} Cross-validation, ROC curve analysis, Confusion matrix, Grid search, Hyperparameter tuning \\
        \vspace{0.15cm}
        \textbf{Deployment:} Docker, Kubernetes, Huggingface Spaces, Vercel, CloudflareCDN \\
        \vspace{0.15cm}
        \textbf{Cloud Platforms:} AWS \\
        \vspace{0.15cm}
        \textbf{Software Development:} Agile methodology, Continuous Integration/Continuous Deployment (CI/CD), GitHub Actions \\
        \vspace{0.15cm}
        \textbf{Database Management:} MySQL, MongoDB, Pincone Vector Database \\
        \vspace{0.15cm}
        \textbf{Version Control:} Git \\
        \vspace{0.15cm}
    }
    }
\end{itemize}


%-----------CERTIFICATIONS---------------
\section{CERTIFICATIONS}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Generative AI with Large Language Models \textcolor{MidnightBlue}{\fontsize{9}{11}\selectfont{\href{https://coursera.org/verify/MAVEJZ9P9AV5}{[MAVEJZ9P9AV5]}}}}{Apr 2024 -- Sep 2023}{DeepLearning.AI And Amazon Web Services}{Coursera.org}
    \resumeSubheading
            {Deep Learning Specialization \textcolor{MidnightBlue}{\fontsize{9}{11}\selectfont{\href{https://coursera.org/verify/specialization/EKJCGU5G2NXF}{[EKJCGU5G2NXF]}}}}{Feb 2024 -- July 2023}{DeepLearning.AI}{Coursera.org}
    \resumeSubheading
            {Machine Learning Specialization \textcolor{MidnightBlue}{\href{https://coursera.org/verify/specialization/2CE3DQW8Z2NG}{{\fontsize{9}{11}\selectfont[2CE3DQW8Z2NG]}}}}{Feb 2024 -- Jun 2023}{Stanford University And DeepLearning.AI}{Coursera.org}
    \resumeSubheading
            {Applied AI with DeepLearning \textcolor{MidnightBlue}{\fontsize{9}{11}\selectfont{\href{https://coursera.org/verify/DRENBUK43NW8}{[DRENBUK43NW8]}}}}{Jan 2022 -- Dec 2021}{IBM}{Coursera.org}
    \resumeSubHeadingListEnd

\vspace{0.1cm}

%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{\href{https://huggingface.co/spaces/ManoharPalanisamy/TextToSQLGenerativeAI}{\textcolor{MidnightBlue}{Gemini Pro: Text-to-SQL Query Generation}}} $|$ \emph{Python, Gemini Pro, SQLite, Streamlit, Huggingface Spaces}} {\href{https://huggingface.co/spaces/ManoharPalanisamy/TextToSQLGenerativeAI}{\textcolor{MidnightBlue}{Live}}}
        \resumeItemListStart
          \resumeItem{Developed an end-to-end project utilizing the Google Generative AI - Gemini Pro Model.}
          \resumeItem{Created a user-friendly interface using Streamlit for text-to-SQL query generation.}
          \resumeItem{Designed and implemented functionality to extract information from SQLite databases based on user input prompts.}
          \resumeItem{Utilized Huggingface Space deployment for seamless integration of AI models, making it accessible via the web at {\href{https://huggingface.co/spaces/ManoharPalanisamy/TextToSQLGenerativeAI}{\textcolor{MidnightBlue}{https://huggingface.co/spaces/ManoharPalanisamy/TextToSQLGenerativeAI}}}}
         \resumeItemListEnd
         \vspace{-13pt}
    
         \resumeProjectHeading
         {\textbf{\href{https://github.com/send2manoo/ChatGPT-MCQ-Generator}{\textcolor{MidnightBlue}{ChatGPT MCQ Generator}}} $|$ \emph{OpenAI API, chatgpt-3.5-turbo, Langchain, Streamlit UI, AWS EC2, Huggingface Spaces}}{}
         \resumeItemListStart
             \resumeItem{Created a modular MCQ Generator using the OpenAI API, chatgpt-3.5-turbo model, Sequential Langchain, and Streamlit UI.}
             \resumeItem{Utilized advanced natural language processing capabilities to get user inputs and subject-specific data to generate multiple-choice questions (MCQs).}
             \resumeItem{Presented MCQs in a user-friendly table format via Streamlit UI and deployed the project on AWS EC2 for accessibility and scalability.}
         \resumeItemListEnd
         \vspace{-13pt}

         \resumeProjectHeading
        {\textbf{\href{https://huggingface.co/spaces/ManoharPalanisamy/InvoiceExtractor}{\textcolor{MidnightBlue}{Gemini Pro Vision: The Future of Invoice Data Extraction}}} $|$ \emph{Python, Gemini Pro Vision, Huggingface Spaces}} {\href{https://huggingface.co/spaces/ManoharPalanisamy/InvoiceExtractor}{\textcolor{MidnightBlue}{Live}}}
        \resumeItemListStart
          \resumeItem{Developed a cutting-edge solution to automate invoice processing using Google Generative AI \\ Gemini Pro Vision Model.}
          \resumeItem{Leveraged image-to-text conversion and advanced NLP techniques to extract key information from invoices with precision and accuracy. I have Used the Streamlit interface for designing the application.}
          \resumeItem{Integrated Huggingface Spaces for deployment and management, making it accessible via the web at {\href{https://huggingface.co/spaces/ManoharPalanisamy/InvoiceExtractor}{\textcolor{MidnightBlue}{https://huggingface.co/spaces/ManoharPalanisamy/InvoiceExtractor}}}}
         \resumeItemListEnd
         \vspace{-13pt}

     
      \resumeProjectHeading
      {\textbf{\href{http://project.decodeai.in}{\textcolor{MidnightBlue}{Image Classifier}}} $|$ \emph{Python, FastAI , Render}} {\href{http://project.decodeai.in}{\textcolor{MidnightBlue}{Live}}}
          \resumeItemListStart
            \resumeItem{Developed an advanced image classifier using the ResNet50 neural network architecture from the Fastai deep learning library.}
            \resumeItem{Trained the model to classify images of Marvel Heroes into 12 distinct classes.}
            \resumeItem{Leveraged the powerful capabilities of Fastai for efficient training and model evaluation.}
           \resumeItem{Hosted the final trained model on Render, making it accessible via the web at  \href{http://project.decodeai.in}{\color{MidnightBlue}{https://project.decodeai.in}}}
           \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {\textbf{\href{https://github.com/send2manoo/Distributed-Deep-Learning}{\textcolor{MidnightBlue}{Distributed Deep Learning with Horovod and MPI}}} $|$ \emph{Python, Horovod, MPI}}{May 2018}
          \resumeItemListStart
            \resumeItem{This project focuses on speeding up deep learning training by distributing the workload across multiple computers.}
            \resumeItem{It uses Horovod, a tool for distributed training, and MPI, a communication protocol. By doing this, we can train models faster and use computing resources more efficiently.}
            \resumeItem{ Through this project, I learned how to use advanced tools to make deep learning training faster and more scalable.}
          \resumeItemListEnd 
        
    \resumeSubHeadingListEnd

%

%-----------TECH BLOG---------------
\section{PERSONAL BLOG}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
         {\textbf{\href{https://www.decodeai.in}{\textcolor{MidnightBlue}{www.decodeai.in}}} $|$ \emph{JAM Stack, Jekyll, Cloudflare, Vercel, ImageKit.io, Umami Analytics, Giscus.app, Crisp }} {\href{https://www.decodeai.in}{\textcolor{MidnightBlue}{Live}}}
        \resumeItemListStart
            \resumeItem{Regularly publish articles on machine learning, deep learning, and other technology-related topics.}
            \resumeItem{Provide valuable resources and insights to fellow tech enthusiasts and learners.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PUBLICATIONS---------------
\section{PUBLICATION}
    \resumeSubHeadingListStart
        \resumeSubheading{Fake Account Eliminator}{March 2015}{National Conference on Engineering Applications for Developing Smart Cities - NCEADS}{}
            \resumeItemListStart
                \resumeItem{This software is designed to find and remove fake accounts on platforms like Facebook, Gmail, and Twitter in India.}
                \resumeItem{It uses the UIDAI (Unique Identification Authority of India) as a key part of its operation.}
                \resumeItem{India has many fake users on social media and email, so this tool helps to identify and eliminate them. It enforces a rule where each person can only have one account, reducing problems for real users and the public.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Engineering in Computer Science }{May 2016}
      {Dhirajlal Gandhi College of Technology, Anna University}{Salem, Tamilnadu}
  \resumeSubHeadingListEnd
  
%-----------Last update-----------
\vspace{100pt} % Adjust vertical space as needed
\begin{center}
    Last update: \today
\end{center}
     
\end{document}
